---
title: "Lisa_Wu_HW_4"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(arrow)
library(ggplot2)
library(broom)
```

## Setting up the data
```{r import saved data, echo=FALSE}
data_path <- "/Users/lisawu/Downloads/"
applications <- read_parquet(paste0(data_path,"exercise_3_applications.parquet"))

applications
```

## create workgroup, clear the NAs in examiner_id
```{r workgroup}
applications <- applications %>%
  mutate(wg = (floor(examiner_art_unit / 10) * 10)) %>%
  mutate(appl_status_date = dmy_hms(appl_status_date)) %>%
  mutate(year = year(appl_status_date)) %>%
  filter(year <= 2017) %>%
  drop_na(examiner_id) 
```

  
## create a new dataframe shows examiner_id, examiner_art_unit, race, year,tc,and wg. Also, drop all NAs in gender and renamed examiner_id as id, and examiner_art_unit as art unit
```{r data-2}
examiners <- applications %>%
  group_by(examiner_id, examiner_art_unit, year) %>%
  drop_na(gender) %>%
  rename(id = examiner_id, art_unit = examiner_art_unit) %>%
  summarise( 
    gender = first(gender),
    race = first(race),
    year = first(year),
    tc = first(tc),
    wg = first(wg)
    )
```
# ```{r print}
# write_csv(examiners, "applications_cleaned.csv")
# ```

## show relationship between tc vs gender 
```{r compare-tcs-by-gender}
library(ggplot2)
plots <- lapply(unique(examiners$tc), function(tc_value) {
  subset_df <- subset(examiners, tc == tc_value)
  filtered_df <- subset_df[!duplicated(subset_df$id), ]
  ggplot(subset_df, aes(x = factor(year), fill = gender)) +
    geom_bar(position="fill") +
    labs(x = "Year", y = "Frequency", fill = "Gender") +
    scale_fill_manual(values = c("blue", "pink")) +
    ggtitle(paste("TC:", tc_value))
})

# Set the layout to a 2x2 grid
layout(matrix(1:4, nrow = 2, ncol = 2))

# Plot each histogram in a separate panel
for (i in 1:4) {
  plot(plots[[i]])
}
```


## show relationship between workgroup vs gender 
```{r compare-workgroups-by-gender}
library(dplyr)
library(tidyr)
# Subset the dataframe for tc = 1600
subset_data <- subset(examiners, tc == 1600)
# Filter out unique wg values
wg_values <- sort(unique(subset_data$wg))
# Generate individual plots for each wg value
for (wg_value in wg_values) {
  # Subset the data for the current wg value
  subset_data_wg <- subset(subset_data, wg == wg_value)
  # Create a new dataframe with counts for each combination of year and gender
  counts <- with(subset_data_wg, table(year, gender))
  # Convert the counts dataframe to long format
  counts_long <- as.data.frame.table(counts)
  # Convert "year" to numeric
  counts_long$year <- as.numeric(as.character(counts_long$year))
  # Expand the data to include all years from 2000 to 2017
  counts_long <- counts_long %>%
    complete(year = min(year):max(year), nesting(gender), fill = list(Freq = 0))
  # Generate the bar plot
  plot <- ggplot(counts_long, aes(x = factor(year), y = Freq, fill = gender)) +
    geom_bar(stat = "identity", position = "fill") +
    scale_fill_manual(values = c("female" = "steelblue", "male" = "orange")) +
    labs(x = "Year", y = "Gender Count", fill = "Gender", title = paste("Workgroup", wg_value)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
  # Save the plot as an individual file (optional)
  ggsave(filename = paste("workgroup", wg_value, ".png", sep = ""), plot = plot)
  # Display the plot
  print(plot)
}

```

## show relationship between art_units vs gender 
```{r compare-art_units-and-gender}

# Select the necessary variables from the examiners dataframe
subset_data <- select(examiners, art_unit, gender, year)

# ratio of gender for each art unit in each year
au_year_ratio <- subset_data %>% 
  group_by(year, art_unit) %>% 
  summarise(percent_female = sum(gender=="female",na.rm = TRUE)/n())

# average ratio of gender across 17 years for each art unit
au_ratio <- au_year_ratio %>% 
  group_by(art_unit) %>% 
  summarise(average_percent_female= mean(percent_female))

# create a new graph
graph <- ggplot(data=au_ratio) +
  geom_col(aes(as.factor(x=art_unit), y = average_percent_female)) 

graph

```

